Grow with the flow: a latitudinal cline in growth rate is associated with more variable precipitation in \textit{Mimulus cardinals}

### 2016-10-13 ms/ms.Rnw
ANOVA tables and more

  mm <- lmer(SER_AbsGrowth ~ AvgGermDay + LER_AbsGrowth + 
               PopID * TempTrt * WaterTrt + (1|Family) + (1|Block), 
             data = master)
	fitSER <- step(mm, reduce.random = F) #includes LER_AbsGrowth, pop, temp, h2o, and temp x h2o

@@

  # Photosynthetic rate
  mm <- lmer(Photo ~ PopID * TempTrt * WaterTrt + (1|Family) + (1|Block),
    data = subset(master, !is.na(master$Photo)))
  fitPhoto <- step(mm, reduce.random = F)

@@

\paragraph{Mortality}
We assayed mortality during twice-weekly growth measurements. We analyzed the probability of surviving until the end of the experiment as a function of population, treatment, and their interactions using a Generalized Linear Mixed Model (GLMM) assuming binomially distributed errors. We included Family and Block as random effects. We assessed significance of fixed effects using Type 2 Analysis of Deviance with Wald \Chi$^2$ tests in the R package \pkg{car} \citep{Fox_Weisberg_2011}.

@@

  library(VSURF)
  # Load VSURF results of climatic variables associated with latitude at cardinalis occurence points
  # Note that occurences have been randomly thinned to account for variation in sampling effort
  load(paste(pathDat, "/clim2lat_fit_t1.RData", sep = "")) # fit_t1
  vsurfLat <- fit_t1

@@

\begin{table}[ht]
   \centering
   \topcaption{Climatic variables}
   \begin{tabular}{@{} ll @{}}
      \toprule
  Climate variable & Abbreviation \\
      \midrule
  % climateWNA VARIABLES:
	DD\_0	& degree-days below 0\celsius (chilling degree-days)  \\
	DD5	  & degree-days above 5\celsius (growing degree-days)   \\
	DD\_18	& degree-days below 18\celsius (heating degree-days)  \\
	DD18	& degree-days above 18\celsius (cooling degree-days)  \\
	NFFD	& number of frost-free days                           \\
	PAS	  & precipitation as snow (mm) between August in previous year and July in current  \\
	Eref	& Hargreaves reference evaporation (mm) \\
	CMD	  & Hargreaves climativ moisture deficit (mm) \\
	MAR   &	mean annual solar radiation (NOTE: removing because too many missing values) \\
	RH    &	mean annual relative humidity \\
  % BIOCLIM VARIABLES:
  bio1	&	Annual Mean Temperature	\\
	bio2	&	Mean Diurnal Range (Mean of monthly (max temp - min temp))	\\
	bio3	&	Isothermality (bio2/bio7) (* 100)	\\
	bio4	&	Temperature Seasonality (standard deviation *100)	\\
	bio5	&	Max Temperature of Warmest Month	\\
	bio6	&	Min Temperature of Coldest Month	\\
	bio7	&	Temperature Annual Range (bio5-bio6)	\\
	bio8	&	Mean Temperature of Wettest Quarter	\\
	bio9	&	Mean Temperature of Driest Quarter	\\
	bio10	&	Mean Temperature of Warmest Quarter	\\
	bio11	&	Mean Temperature of Coldest Quarter	\\
	bio12	&	Annual Precipitation	\\
	bio15	&	Precipitation Seasonality (Coefficient of Variation)	\\
	bio16	&	Precipitation of Wettest Quarter	\\
	bio17	&	Precipitation of Driest Quarter	\\
	bio18	&	Precipitation of Warmest Quarter	\\
	bio19	&	Precipitation of Coldest Quarter	\\
	    \bottomrule
   \end{tabular}
   \label{table:TableS_ClimVars}
\end{table}

% ANOVA table for LER (need to label tables)

<<TableS_fitLER, echo=FALSE, results=hide, warning=FALSE, message=FALSE>>=
	  source(paste(pathMS, "/functions.R", sep = ""))

  ss <- sigDig(fitLER$anova.table$`Sum Sq`)
  ms <- sigDig(fitLER$anova.table$`Mean Sq`)
  df1 <- sigDig(fitLER$anova.table$NumDF)
  df2 <- sigDig(fitLER$anova.table$DenDF)
  fval <- sigDig(fitLER$anova.table$F.value)
 pval <- pval2latex(fitLER$anova.table$`Pr(>F)`)
@

\begin{table}[htbp]
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[ANOVA table, leaf expansion rate]{CAPTION}
	\begin{center}
	\begin{tabular}{lcccccc}
	\toprule

                     & SS & MS & df1 & df2 & \em{F} & $P$ \\ \midrule
  Day of Germination & 18.2 & 18.2 & 1 & 633.1 & 35.2 & 4.78 $\times10^{-9}$ \\
mmLER

Population & 22.3 & 1.5 & 15 & 121.5 & 4.3 & 2.57 $\times10^{-6}$ \\
Temperature & 114.4 & 114.4 & 1 & 567.7 & 352.3 & 1.64 $\times10^{-61}$ \\
Water & 4.2 & 4.2 & 1 & 567.7 & 12.6 & 4.12 $\times10^{-4}$ \\
Population $\times$ Temperature & 3.1 & 0.2 & 15 & 553.3 & 0.6 & 0.86 \\
Population $\times$ Water & 8.9 & 0.6 & 15 & 567.8 & 1.8 & 0.03 \\
Temperature $\times$ Water & 0 & 0 & 1 & 550.5 & 0 & 0.99 \\
Population $\times$ Temperature $\times$ Water & 4 & 0.3 & 15 & 535.4 & 0.8 & 0.69 \\

	\bottomrule
	\end{tabular}
	\label{table:TableS_fitLER}
	\end{center}
\end{table}

% ANOVA table for SER (need to label tables)
\begin{table}[htbp]
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[ANOVA table, shoot elongation rate]{CAPTION}
	\begin{center}
	\begin{tabular}{lcccccc}
	\toprule

	\input{Tables/Table_heightGrowthAnova.txt}

	\bottomrule
	\end{tabular}
	\end{center}
\end{table}

>>>>

	# Mixed model including LER_AbsGrowth as covariate
  # mm <- lmer(SER_AbsGrowth ~ AvgGermDay + LER_AbsGrowth + 
  #             PopID * TempTrt * WaterTrt + (1|Family) + (1|Block), 
  #           data = master)
	# fitSER <- step(mm, reduce.random = F) #includes LER_AbsGrowth, pop, temp, h2o, and temp x h2o

	# Mixed model without LER_AbsGrowth as covariate
  mm <- lmer(SER_AbsGrowth ~ AvgGermDay + 
               PopID * TempTrt * WaterTrt + (1|Family) + (1|Block), 
             data = master)
	fitSER <- step(mm, reduce.random = F)

@@

  # Photosynthetic rate (remove is satisfied w/ resPhoto analysis)
  mm <- lmer(Photo ~ PopID * TempTrt * WaterTrt + (1|Family) + (1|Block),
    data = subset(master, !is.na(master$Photo)))
    fitPhoto <- step(mm, reduce.random = F)

@@

\paragraph{Mortality}
We assayed mortality during twice-weekly growth measurements. We analyzed the probability of surviving until the end of the experiment as a function of population, treatment, and their interactions using a Generalized Linear Mixed Model (GLMM) assuming binomially distributed errors. We included Family and Block as random effects. We assessed significance of fixed effects using Type 2 Analysis of Deviance with Wald $\chi ^2$ tests in the R package \pkg{car} \citep{Fox_Weisberg_2011}.

@@

  library(VSURF)

  # Load VSURF results of climatic variables associated with latitude at cardinalis occurence points
  # Note that occurences have been randomly thinned to account for variation in sampling effort
  load(paste(pathDat, "/clim2lat_fit_t1.RData", sep = "")) # fit_t1
  vsurfLat <- fit_t1

@@

\begin{table}[ht]
   \centering
   \topcaption{Climatic variables}
   \begin{tabular}{@{} ll @{}}
      \toprule
   Abbreviation & Climate variable \\
      \midrule
  % climateWNA VARIABLES:
	DD\_0	& degree-days below 0\celsius (chilling degree-days)  \\
	DD5	  & degree-days above 5\celsius (growing degree-days)   \\
	DD\_18	& degree-days below 18\celsius (heating degree-days)  \\
	DD18	& degree-days above 18\celsius (cooling degree-days)  \\
	NFFD	& number of frost-free days                           \\
	PAS	  & precipitation as snow (mm) between August in previous year and July in current  \\
	Eref	& Hargreaves reference evaporation (mm) \\
	CMD	  & Hargreaves climatic moisture deficit (mm) \\
	RH    &	mean annual relative humidity \\
  % BIOCLIM VARIABLES:
  bio1	&	Annual Mean Temperature	\\
	bio2	&	Mean Diurnal Range (Mean of monthly (max temp - min temp))	\\
	bio3	&	Isothermality (bio2/bio7) (* 100)	\\
	bio4	&	Temperature Seasonality (standard deviation *100)	\\
	bio5	&	Max Temperature of Warmest Month	\\
	bio6	&	Min Temperature of Coldest Month	\\
	bio7	&	Temperature Annual Range (bio5-bio6)	\\
	bio8	&	Mean Temperature of Wettest Quarter	\\
	bio9	&	Mean Temperature of Driest Quarter	\\
	bio10	&	Mean Temperature of Warmest Quarter	\\
	bio11	&	Mean Temperature of Coldest Quarter	\\
	bio12	&	Annual Precipitation	\\
	bio15	&	Precipitation Seasonality (Coefficient of Variation)	\\
	bio16	&	Precipitation of Wettest Quarter	\\
	bio17	&	Precipitation of Driest Quarter	\\
	bio18	&	Precipitation of Warmest Quarter	\\
	bio19	&	Precipitation of Coldest Quarter	\\
	    \bottomrule
   \end{tabular}
   \label{table:TableS_ClimVars}
\end{table}

% ANOVA table for LER

<<TableS_fitLER, echo=FALSE, results=hide, warning=FALSE, message=FALSE>>=

  # this is sourced above. remove from here once testing is over  
  source(paste(pathMS, "/functions.R", sep = ""))

  # Convert numbers from R to LaTeX characters
  lerTab <- data.frame(ss = sigDig(fitLER$anova.table$`Sum Sq`),
                       ms = sigDig(fitLER$anova.table$`Mean Sq`),
                       df1 = sigDig(fitLER$anova.table$NumDF),
                       df2 = sigDig(fitLER$anova.table$DenDF),
                       fval = sigDig(fitLER$anova.table$F.value),
                       pval = pval2latex(fitLER$anova.table$`Pr(>F)`),
                       stringsAsFactors = F)
  rownames(lerTab) <- rownames(fitLER$anova.table)

\begin{table}[htbp]
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[ANOVA table, leaf expansion rate]{Sum of squares (SS); Mean sum of squares (MS); Numerator degrees of freedom (df1); Denominator degrees of freedom (df2); }
	\begin{center}
	\begin{tabular}{lcccccc}
	\toprule

  & SS & MS & df1 & df2 & \em{F}-value & $P$-value \\ \midrule
  Day to Germination & \Sexpr{lerTab["AvgGermDay", "ss"]} & 
    \Sexpr{lerTab["AvgGermDay", "ms"]} & \Sexpr{lerTab["AvgGermDay", "df1"]} & 
    \Sexpr{lerTab["AvgGermDay", "df2"]} & \Sexpr{lerTab["AvgGermDay", "fval"]} &
    \Sexpr{lerTab["AvgGermDay", "pval"]} \\
  Population & \Sexpr{lerTab["PopID", "ss"]} & \Sexpr{lerTab["PopID", "ms"]} & 
    \Sexpr{lerTab["PopID", "df1"]} & \Sexpr{lerTab["PopID", "df2"]} & 
    \Sexpr{lerTab["PopID", "fval"]} & \Sexpr{lerTab["PopID", "pval"]} \\
  Temperature & \Sexpr{lerTab["TempTrt", "ss"]} & 
    \Sexpr{lerTab["TempTrt", "ms"]} & \Sexpr{lerTab["TempTrt", "df1"]} &
    \Sexpr{lerTab["TempTrt", "df2"]} & \Sexpr{lerTab["TempTrt", "fval"]} &
    \Sexpr{lerTab["TempTrt", "pval"]} \\
  Water & \Sexpr{lerTab["WaterTrt", "ss"]} & \Sexpr{lerTab["WaterTrt", "ms"]} & 
    \Sexpr{lerTab["WaterTrt", "df1"]} & \Sexpr{lerTab["WaterTrt", "df2"]} & 
    \Sexpr{lerTab["WaterTrt", "fval"]} & \Sexpr{lerTab["WaterTrt", "pval"]} \\
  Population $\times$ Temperature & \Sexpr{lerTab["PopID:TempTrt", "ss"]} & 
    \Sexpr{lerTab["PopID:TempTrt", "ms"]} & 
    \Sexpr{lerTab["PopID:TempTrt", "df1"]} & 
    \Sexpr{lerTab["PopID:TempTrt", "df2"]} & 
    \Sexpr{lerTab["PopID:TempTrt", "fval"]} &
    \Sexpr{lerTab["PopID:TempTrt", "pval"]} \\
  Population $\times$ Water & \Sexpr{lerTab["PopID:WaterTrt", "ss"]} & 
    \Sexpr{lerTab["PopID:WaterTrt", "ms"]} & 
    \Sexpr{lerTab["PopID:WaterTrt", "df1"]} &
    \Sexpr{lerTab["PopID:WaterTrt", "df2"]} &
    \Sexpr{lerTab["PopID:WaterTrt", "fval"]} & 
    \Sexpr{lerTab["PopID:WaterTrt", "pval"]} \\
  Population $\times$ Temperature $\times$ Water & 
    \Sexpr{lerTab["PopID:TempTrt:WaterTrt", "ss"]} & 
    \Sexpr{lerTab["PopID:TempTrt:WaterTrt", "ms"]} & 
    \Sexpr{lerTab["PopID:TempTrt:WaterTrt", "df1"]} & 
    \Sexpr{lerTab["PopID:TempTrt:WaterTrt", "df2"]} & 
    \Sexpr{lerTab["PopID:TempTrt:WaterTrt", "fval"]} & 
    \Sexpr{lerTab["PopID:TempTrt:WaterTrt", "pval"]} \\
	\bottomrule
	\end{tabular}
	\label{table:TableS_fitLER}
	\end{center}
\end{table}

% ANOVA table for SER

<<TableS_fitSER, echo=FALSE, results=hide, warning=FALSE, message=FALSE>>=

  # Convert numbers from R to LaTeX characters
  serTab <- data.frame(ss = sigDig(fitSER$anova.table$`Sum Sq`),
                       ms = sigDig(fitSER$anova.table$`Mean Sq`),
                       df1 = sigDig(fitSER$anova.table$NumDF),
                       df2 = sigDig(fitSER$anova.table$DenDF),
                       fval = sigDig(fitSER$anova.table$F.value),
                       pval = pval2latex(fitSER$anova.table$`Pr(>F)`),
                       stringsAsFactors = F)
  rownames(serTab) <- rownames(fitSER$anova.table)

\begin{table}[htbp]
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[ANOVA table, shoot elongation rate]{Sum of squares (SS); Mean sum of squares (MS); Numerator degrees of freedom (df1); Denominator degrees of freedom (df2)}
	\begin{center}
	\begin{tabular}{lcccccc}
	\toprule

  & SS & MS & df1 & df2 & \em{F}-value & $P$-value \\ \midrule
  Day to Germination & \Sexpr{serTab["AvgGermDay", "ss"]} & 
    \Sexpr{serTab["AvgGermDay", "ms"]} & \Sexpr{serTab["AvgGermDay", "df1"]} & 
    \Sexpr{serTab["AvgGermDay", "df2"]} & \Sexpr{serTab["AvgGermDay", "fval"]} &
    \Sexpr{serTab["AvgGermDay", "pval"]} \\
  Population & \Sexpr{serTab["PopID", "ss"]} & \Sexpr{serTab["PopID", "ms"]} & 
    \Sexpr{serTab["PopID", "df1"]} & \Sexpr{serTab["PopID", "df2"]} & 
    \Sexpr{serTab["PopID", "fval"]} & \Sexpr{serTab["PopID", "pval"]} \\
  Temperature & \Sexpr{serTab["TempTrt", "ss"]} & 
    \Sexpr{serTab["TempTrt", "ms"]} & \Sexpr{serTab["TempTrt", "df1"]} &
    \Sexpr{serTab["TempTrt", "df2"]} & \Sexpr{serTab["TempTrt", "fval"]} &
    \Sexpr{serTab["TempTrt", "pval"]} \\
  Water & \Sexpr{serTab["WaterTrt", "ss"]} & \Sexpr{serTab["WaterTrt", "ms"]} & 
    \Sexpr{serTab["WaterTrt", "df1"]} & \Sexpr{serTab["WaterTrt", "df2"]} & 
    \Sexpr{serTab["WaterTrt", "fval"]} & \Sexpr{serTab["WaterTrt", "pval"]} \\
  Population $\times$ Temperature & \Sexpr{serTab["PopID:TempTrt", "ss"]} & 
    \Sexpr{serTab["PopID:TempTrt", "ms"]} & 
    \Sexpr{serTab["PopID:TempTrt", "df1"]} & 
    \Sexpr{serTab["PopID:TempTrt", "df2"]} & 
    \Sexpr{serTab["PopID:TempTrt", "fval"]} &
    \Sexpr{serTab["PopID:TempTrt", "pval"]} \\
  Population $\times$ Water & \Sexpr{serTab["PopID:WaterTrt", "ss"]} & 
    \Sexpr{serTab["PopID:WaterTrt", "ms"]} & 
    \Sexpr{serTab["PopID:WaterTrt", "df1"]} &
    \Sexpr{serTab["PopID:WaterTrt", "df2"]} &
    \Sexpr{serTab["PopID:WaterTrt", "fval"]} & 
    \Sexpr{serTab["PopID:WaterTrt", "pval"]} \\
  Population $\times$ Temperature $\times$ Water & 
    \Sexpr{serTab["PopID:TempTrt:WaterTrt", "ss"]} & 
    \Sexpr{serTab["PopID:TempTrt:WaterTrt", "ms"]} & 
    \Sexpr{serTab["PopID:TempTrt:WaterTrt", "df1"]} & 
    \Sexpr{serTab["PopID:TempTrt:WaterTrt", "df2"]} & 
    \Sexpr{serTab["PopID:TempTrt:WaterTrt", "fval"]} & 
    \Sexpr{serTab["PopID:TempTrt:WaterTrt", "pval"]} \\
	\bottomrule
	\end{tabular}
	\label{table:TableS_fitSER}
	\end{center}
\end{table}

% ANOVA table for photosynthesis

<<TableS_fitPhoto, echo=FALSE, results=hide, warning=FALSE, message=FALSE>>=

  # Convert numbers from R to LaTeX characters
  photoTab <- data.frame(ss = sigDig(fitPhoto$anova.table$`Sum Sq`),
                         ms = sigDig(fitPhoto$anova.table$`Mean Sq`),
                         df1 = sigDig(fitPhoto$anova.table$NumDF),
                         df2 = sigDig(fitPhoto$anova.table$DenDF),
                         fval = sigDig(fitPhoto$anova.table$F.value),
                         pval = pval2latex(fitPhoto$anova.table$`Pr(>F)`),
                         stringsAsFactors = F)
  rownames(photoTab) <- rownames(fitPhoto$anova.table)

\begin{table}[htbp]
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[ANOVA table, photosynthesis]{Sum of squares (SS); Mean sum of squares (MS); Numerator degrees of freedom (df1); Denominator degrees of freedom (df2)}
	\begin{center}
	\begin{tabular}{lcccccc}
	\toprule

  & SS & MS & df1 & df2 & \em{F}-value & $P$-value \\ \midrule
  Population & \Sexpr{photoTab["PopID", "ss"]} & 
    \Sexpr{photoTab["PopID", "ms"]} & \Sexpr{photoTab["PopID", "df1"]} &
    \Sexpr{photoTab["PopID", "df2"]} & \Sexpr{photoTab["PopID", "fval"]} &
    \Sexpr{photoTab["PopID", "pval"]} \\
  Temperature & \Sexpr{photoTab["TempTrt", "ss"]} & 
    \Sexpr{photoTab["TempTrt", "ms"]} & \Sexpr{photoTab["TempTrt", "df1"]} &
    \Sexpr{photoTab["TempTrt", "df2"]} & \Sexpr{photoTab["TempTrt", "fval"]} &
    \Sexpr{photoTab["TempTrt", "pval"]} \\
  Water & \Sexpr{photoTab["WaterTrt", "ss"]} & 
    \Sexpr{photoTab["WaterTrt", "ms"]} & \Sexpr{photoTab["WaterTrt", "df1"]} &
    \Sexpr{photoTab["WaterTrt", "df2"]} & \Sexpr{photoTab["WaterTrt", "fval"]} &
    \Sexpr{photoTab["WaterTrt", "pval"]} \\
  Population $\times$ Temperature & \Sexpr{photoTab["PopID:TempTrt", "ss"]} & 
    \Sexpr{photoTab["PopID:TempTrt", "ms"]} & 
    \Sexpr{photoTab["PopID:TempTrt", "df1"]} & 
    \Sexpr{photoTab["PopID:TempTrt", "df2"]} & 
    \Sexpr{photoTab["PopID:TempTrt", "fval"]} &
    \Sexpr{photoTab["PopID:TempTrt", "pval"]} \\
  Population $\times$ Water & \Sexpr{photoTab["PopID:WaterTrt", "ss"]} & 
    \Sexpr{photoTab["PopID:WaterTrt", "ms"]} & 
    \Sexpr{photoTab["PopID:WaterTrt", "df1"]} &
    \Sexpr{photoTab["PopID:WaterTrt", "df2"]} &
    \Sexpr{photoTab["PopID:WaterTrt", "fval"]} & 
    \Sexpr{photoTab["PopID:WaterTrt", "pval"]} \\
  Population $\times$ Temperature $\times$ Water & 
    \Sexpr{photoTab["PopID:TempTrt:WaterTrt", "ss"]} & 
    \Sexpr{photoTab["PopID:TempTrt:WaterTrt", "ms"]} & 
    \Sexpr{photoTab["PopID:TempTrt:WaterTrt", "df1"]} & 
    \Sexpr{photoTab["PopID:TempTrt:WaterTrt", "df2"]} & 
    \Sexpr{photoTab["PopID:TempTrt:WaterTrt", "fval"]} & 
    \Sexpr{photoTab["PopID:TempTrt:WaterTrt", "pval"]} \\
	\bottomrule
	\end{tabular}
	\label{table:TableS_fitPhoto}
	\end{center}
\end{table}

% ANOVA table for intrinsic photosynthetic rate

<<TableS_fitIntrnPhoto, echo=FALSE, results=hide, warning=FALSE, message=FALSE>>=

  # Convert numbers from R to LaTeX characters
  intrnPhotoTab <- data.frame(ss = sigDig(fitIntrnPhoto$anova.table$`Sum Sq`),
                              ms = sigDig(fitIntrnPhoto$anova.table$`Mean Sq`),
                              df1 = sigDig(fitIntrnPhoto$anova.table$NumDF),
                              df2 = sigDig(fitIntrnPhoto$anova.table$DenDF),
                              fval = sigDig(fitIntrnPhoto$anova.table$F.value),
                              pval = 
                                pval2latex(fitIntrnPhoto$anova.table$`Pr(>F)`),
                              stringsAsFactors = F)
  rownames(intrnPhotoTab) <- rownames(fitIntrnPhoto$anova.table)

\begin{table}[htbp]
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[ANOVA table, photosynthesis]{Sum of squares (SS); Mean sum of squares (MS); Numerator degrees of freedom (df1); Denominator degrees of freedom (df2)}
	\begin{center}
	\begin{tabular}{lcccccc}
	\toprule

  & SS & MS & df1 & df2 & \em{F}-value & $P$-value \\ \midrule
  Population & \Sexpr{photoTab["PopID", "ss"]} & 
    \Sexpr{intrnPhotoTab["PopID", "ms"]} & 
    \Sexpr{intrnPhotoTab["PopID", "df1"]} &
    \Sexpr{intrnPhotoTab["PopID", "df2"]} & 
    \Sexpr{intrnPhotoTab["PopID", "fval"]} &
    \Sexpr{intrnPhotoTab["PopID", "pval"]} \\
  Temperature & \Sexpr{intrnPhotoTab["TempTrt", "ss"]} & 
    \Sexpr{intrnPhotoTab["TempTrt", "ms"]} & 
    \Sexpr{intrnPhotoTab["TempTrt", "df1"]} &
    \Sexpr{intrnPhotoTab["TempTrt", "df2"]} & 
    \Sexpr{intrnPhotoTab["TempTrt", "fval"]} &
    \Sexpr{intrnPhotoTab["TempTrt", "pval"]} \\
  Water & \Sexpr{intrnPhotoTab["WaterTrt", "ss"]} & 
    \Sexpr{intrnPhotoTab["WaterTrt", "ms"]} & 
    \Sexpr{intrnPhotoTab["WaterTrt", "df1"]} &
    \Sexpr{intrnPhotoTab["WaterTrt", "df2"]} & 
    \Sexpr{intrnPhotoTab["WaterTrt", "fval"]} &
    \Sexpr{intrnPhotoTab["WaterTrt", "pval"]} \\
  Population $\times$ Temperature & 
    \Sexpr{intrnPhotoTab["PopID:TempTrt", "ss"]} & 
    \Sexpr{intrnPhotoTab["PopID:TempTrt", "ms"]} & 
    \Sexpr{intrnPhotoTab["PopID:TempTrt", "df1"]} & 
    \Sexpr{intrnPhotoTab["PopID:TempTrt", "df2"]} & 
    \Sexpr{intrnPhotoTab["PopID:TempTrt", "fval"]} &
    \Sexpr{intrnPhotoTab["PopID:TempTrt", "pval"]} \\
  Population $\times$ Water & \Sexpr{intrnPhotoTab["PopID:WaterTrt", "ss"]} & 
    \Sexpr{intrnPhotoTab["PopID:WaterTrt", "ms"]} & 
    \Sexpr{intrnPhotoTab["PopID:WaterTrt", "df1"]} &
    \Sexpr{intrnPhotoTab["PopID:WaterTrt", "df2"]} &
    \Sexpr{intrnPhotoTab["PopID:WaterTrt", "fval"]} & 
    \Sexpr{intrnPhotoTab["PopID:WaterTrt", "pval"]} \\
  Population $\times$ Temperature $\times$ Water & 
    \Sexpr{intrnPhotoTab["PopID:TempTrt:WaterTrt", "ss"]} & 
    \Sexpr{intrnPhotoTab["PopID:TempTrt:WaterTrt", "ms"]} & 
    \Sexpr{intrnPhotoTab["PopID:TempTrt:WaterTrt", "df1"]} & 
    \Sexpr{intrnPhotoTab["PopID:TempTrt:WaterTrt", "df2"]} & 
    \Sexpr{intrnPhotoTab["PopID:TempTrt:WaterTrt", "fval"]} & 
    \Sexpr{intrnPhotoTab["PopID:TempTrt:WaterTrt", "pval"]} \\
	\bottomrule
	\end{tabular}
	\label{table:TableS_fitIntrnPhoto}
	\end{center}
\end{table}

% Analysis of deviance table for mortality

<<TableS_fitPhoto, echo=FALSE, results=hide, warning=FALSE, message=FALSE>>=

  # Convert numbers from R to LaTeX characters
  tab <- Anova(fitMort, type = 2)
  mortTab <- data.frame(chisq = sigDig(tab$Chisq), df = tab$Df,
                         pval = pval2latex(tab$`Pr(>Chisq)`),
                         stringsAsFactors = F)
  rownames(mortTab) <- rownames(tab)

\begin{table}[htbp]
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[ANOVA table, mortality]{CAPTION}
	\begin{center}
	\begin{tabular}{lccc}
	\toprule

  & $\chi ^2$ & df & $P$-value \\ \midrule
  Population & \Sexpr{mortTab["PopID", "chisq"]} & 
    \Sexpr{mortTab["PopID", "df"]} & \Sexpr{mortTab["PopID", "pval"]} & \\
  Temperature & \Sexpr{mortTab["TempTrt", "chisq"]} & 
    \Sexpr{mortTab["TempTrt", "df"]} & \Sexpr{mortTab["TempTrt", "pval"]} & \\
  Water & \Sexpr{mortTab["WaterTrt", "chisq"]} & 
    \Sexpr{mortTab["WaterTrt", "df"]} & \Sexpr{mortTab["WaterTrt", "pval"]} & \\
  Population $\times$ Temperature & \Sexpr{mortTab["PopID:TempTrt", "chisq"]} & 
    \Sexpr{mortTab["PopID:TempTrt", "df"]} & 
    \Sexpr{mortTab["PopID:TempTrt", "pval"]} & \\
  Population $\times$ Water & \Sexpr{mortTab["PopID:WaterTrt", "chisq"]} & 
    \Sexpr{mortTab["PopID:WaterTrt", "df"]} & 
    \Sexpr{mortTab["PopID:WaterTrt", "pval"]} & \\
  Population $\times$ Temperature $\times$ Water & 
    \Sexpr{mortTab["PopID:TempTrt:WaterTrt", "chisq"]} & 
    \Sexpr{mortTab["PopID:TempTrt:WaterTrt", "df"]} & 
    \Sexpr{mortTab["PopID:TempTrt:WaterTrt", "pval"]} & \\	\bottomrule
	\end{tabular}
	\label{table:TableS_fitMort}
	\end{center}
\end{table}
